\textbf{Designing a Security Management Layer for CDN Assets}

### 2016-02-15 tex/paper.tex
Added Implementation introduction

\newpage
\label{sec:model}
\section{Model}
The model for this work should show how the data can not be accessed or modified by unauthorized
users and how the integrity of the data is always kept in the Perius system.

There could also be another relevant part included in the model, to show that content can not be 
accessed by unauthorized viewers once the content is uploaded to a CDN. But as that should already 
have been thoroughly checked by the CDN providers this work can focus solely on the internal users 
and content of the management system.

\subsection{Related work}
The model for this paper is based on the work that was done by Bell, D Elliott, LaPadula and Leonard
J in their papers Secure computer systems: Mathematical foundations~\cite{BLP1} and Secure computer
systems: A mathematical model~\cite{BLP2}. In these papers the foundation was laid for how to model
a computer system to be able to analyse the security of a system. Furthermore this paper was also 
inspired by Biba, Integrity considerations for secure computer systems~\cite{BIBA}, where many of 
the points made by him was taken into consideration when inspecting that the integrity of the data 
was always sound.

@@

\newpage
\section{Implementation} \label{sec:implementation}
\subsection{Background}
\subsubsection{The current system} \label{sec:current_system}
Today a system called battlebinary~\cite{BATTLEBINARY} is used for managing and uploading files,
mostly images, to content delivery networks. The current system does not make use out of the
security features that the CDN's are offering, instead it uses a form of security by obscurity. When
a file is uploaded to a CDN it is open for the public, but its filename is composed out of its
original filename concatenated with a part of the MD5 hash of the content of the file, which makes
it an extremely hard process to access the file on the CDN without access to the original file or a
reference to the URI.

>>>>

\newpage
\label{sec:model}
\section{Model} \label{sec:model}
The model for this work should show how the data can not be accessed or modified by unauthorized
users and how the defined integrity of the data is always kept in the Perius system.

There could also be another relevant part included in the model, to show that content can not be 
accessed by unauthorized viewers once the content is uploaded to a CDN. But as that should already 
have been thoroughly checked by the CDN providers this work can focus solely on the internal users 
and content in the management system.

\subsection{Related work}
The model for this paper is based on the work that was done by Bell, D Elliott, LaPadula and 
Leonard J in their papers \textit{Secure computer systems: Mathematical foundations}~\cite{BLP1} 
and \textit{Secure computer systems: A mathematical model}~\cite{BLP2}. 
In these papers the foundation was laid for how to model a computer system to be able to analyse 
the security of a system. Furthermore this paper was also inspired by Biba, \textit{Integrity 
considerations for secure computer systems}~\cite{BIBA}, where many of the points made by him was 
taken into consideration when inspecting that the integrity of the data was always sound.

@@

\newpage
\section{Implementation} \label{sec:implementation}
This chapter deals with the second part of this work, namely the implementation of the Perius 
system based which is based on the model described in Section~\ref{sec:model}. As this work is not
intended as a instructions manual more information about how to deploy and use Perius can be found
on \url{http://perius.se}. This chapter's focus is instead on how the decisions for the
implementation were made, how well the system would scale and the resulting security implications.

\subsection{Background}
\subsubsection{The current system} \label{sec:current_system}
Today a system called battlebinary~\cite{BATTLEBINARY} is used for managing and uploading files,
mostly images, to content delivery networks. The current system does not make use out of the
security features that the CDN's are offering, instead it uses a form of security by obscurity. When
a file is uploaded to a CDN it is open for the public, but its filename is composed out of its
original filename concatenated with a part of the MD5 hash of the content of the file, which makes
it an extremely hard process to access the file on the CDN without access to the original file or a
reference to the URI.
